---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rcaladapt

<!-- badges: start -->
<!-- badges: end -->

The goal of rcaladapt is to access climate data from Cal-Adapt, including historical and projected climate data for specific coordinates.

## Installation

You can install the development version of rcaladapt from [Github](https://github.com/kdybala/rcaladapt) with:

``` r
devtools::install_github("kdybala/rcaladapt")
```
<!-- You can install the released version of rcaladapt from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rcaladapt") -->
<!-- ``` -->

## Example

Extract projected annual precipitation for the RCP 4.5 scenario, from the HadGEM2-ES model, for specific coordinates: 

```{r example1}
library(rcaladapt)
example1 <- query_caladapt(var = 'pr', scenario = 'rcp45', model = 'HadGEM2-ES', 
                          coords = '-122.545886,38.248392')
# convert from inches/day to inches/yr
example1$data <- example1$data * 365
head(example1)
```

The function returns a tibble, to facilitate further analysis and plotting:

```{r plot1, echo = FALSE}
library(ggplot2)
ggplot(example1, aes(index, data)) + geom_line() + xlab('Year') + 
  ylab('precipitation (in/yr)')
```

Use purrr::map functions to repeat for several climate models, scenarios, or variables:

```{r example2}
models <- c('HadGEM2-ES', 'CNRM-CM5', 'CanESM2', 'MIROC5', 'livneh')

example2 <- purrr::map_dfr(models, .f = function(x) {
  query_caladapt(var = 'tasmin', scenario = 'rcp85', model = x, 
                 coords = '-122.545886,38.248392')
})
ggplot(example2, aes(index, data)) + geom_line(aes(color = model)) + 
  ylab('Minimum Temperature (F)') + xlab('Year')
```

<!-- In that case, don't forget to commit and push the resulting figure files, so they display on GitHub! -->
